Lifting CDCL to Relational Domains

### 2016-10-15 experiments.tex
figure 1

\paragraph {\em \textbf{Decision Heuristics}} We compare the performance of 
different decision heuristic on our benchmarks.  We observe that 
the ordered heuristic outperforms other heuristics on control-intensive 
benchmarks due to its ability to prioritize decisions on variables that 
appears in conditional branches.  For straight-line code and most of 
the bit-vector regression suite, random heuristics performs the best.  
Whereas, the activity based heuristics such as Berkmin heuristic which 
works well in propositional cases performs best for benchmarks that 
encountered the maximum number of conflicts to prove safety, thus allowing 
the heuristics to choose the decison variable from the set of learnt clauses.

>>>>

\paragraph {\em \textbf{Decision Heuristics}} We compare the performance of 
different decision heuristic on our benchmarks.  We observe that 
the ordered heuristic outperforms other heuristics on control-intensive 
benchmarks due to its ability to prioritize decisions on variables that 
appears in conditional branches.  For straight-line code and most of 
the bit-vector regression suite, random heuristics performs the best.  
Whereas, the activity based heuristics such as Berkmin heuristic which 
works well in propositional cases performs best for benchmarks that 
encountered the maximum number of conflicts to prove safety, thus allowing 
the heuristics to choose the decison variable among the set of learnt clauses.
